### 2021-07-05 src/paper/appendix_data.tex
Replace Smith pre-print with published version.

We sample households to build our synthetic population of over one million households
keeping for each individual their age, gender, occupation and whether they work on
Saturdays and Sundays. For each household we draw its county and set the corresponding
federal state.% county is not part of the microcensus campus file
We draw for young children whether they attend a nursery or not
\citep{Destatis2020}.\comment[id=K]{Missing still:
    \begin{itemize}
        \item describe how we create the contact model group ids for school,
        work and other
        \item describe work contact priority, educ contact priority and
        rapid test compliance parameter and quarantine compliance.
        \item vaccination rank creation
    \end{itemize}
}

>>>>

We sample households to build our synthetic population of over one million households
keeping for each individual their age, gender, occupation and whether they work on
Saturdays and Sundays. For each household we draw its county and set the corresponding
federal state.% county is not part of the microcensus campus file
We draw for young children whether they attend a nursery or
not.\citep{Destatis2020}.\comment[id=K]{Missing still:
    \begin{itemize}
        \item describe how we create the contact model group ids for school,
        work and other
        \item describe work contact priority, educ contact priority and
        rapid test compliance parameter and quarantine compliance.
        \item vaccination rank creation
    \end{itemize}
}

### 2021-07-05 src/paper/model/estimated_parameters.tex
Remove all comments by hand for arxiv.
Put comments back in.
Add comments by Philipp Eisenhauer.
Replace Smith pre-print with published version.

\subsection{Estimated Parameters}
\label{subsec:estimated_params}

@@

To avoid over-fitting and simplify the numerical optimization problem, we only allow for
five different infection probabilities: 1) for contacts in schools 2) contacts in
preschools and nurseries. 3) for work contacts. 4) for households. 5) for other
contacts.\comment[id=J]{Write that the exact numbers are hard to interpret and show
the infections by channel heatmap more prominently than the infection probabilities}

>>>>

\subsection{Estimated Parameters}\comment[id=K]{Philipp suggests to write more about
identification. Both in general and to take seasonality as an example of how we identify
both calibrated and estimated parameters. }
\label{subsec:estimated_params}

@@

To avoid over-fitting and simplify the numerical optimization problem, we only allow for
five different infection probabilities: 1) for contacts in schools 2) contacts in
preschools and nurseries. 3) for work contacts. 4) for households. 5) for other
contacts.\comment[id=J]{Write that the exact numbers are hard to interpret and show the
infections by channel heatmap more prominently than the infection
probabilities}\comment[id=K]{Compare to
\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3867682}{these estimates}}
